TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-14 paper/paper.tex
Added some figures

In our results, we see that all algorithms clearly respond to the simulated
network circumstances, but not very much to each other. Most algorithms are
fair towards all other algorithms.

@@

On top of this, CTCP also lowers its speed in response to the simulated network
circumstances: with 1.2\% packet loss and 8 milliseconds latency, it will reach
around 25 megabits, and with 290 milliseconds latency and no loss, it reaches
around 1.5 megabits.

BBR is unique in that it barely responds to packet loss but only to delay: even
with 1.2\% loss, as long as the delay is low (8 milliseconds in our case), it
reaches 850$\pm$20 megabits per second. Other algorithms will reach much lower
speeds, but we see no signs of BBR being the cause of that. In tests that
involve two algorithms that are neither BBR nor CTCP, speeds are not higher
than with BBR being one of the two algorithms. %TODO check this one (this was gut feeling, but looking at the data, there might be a slight effect that BBR has on things)

>>>>

In our results, we see that all algorithms clearly respond to the simulated
network circumstances, but not very much to each other. Most algorithms are
fair towards all other algorithms and will use their half of the connection.
See figures \ref{fig:fair-1} and \ref{fig:fair-2}.

\begin{figure}[H]
	\makebox[\textwidth]{
		\centering
		\begin{minipage}{0.5\paperwidth}
			\centering
			\includegraphics[width=0.9\textwidth]{figs/cubic-bic-8-0.png}
			\caption{CUBIC vs BIC with 8ms latency and 0\% loss}
			\label{fig:fair-1}
		\end{minipage}\hfill
		\begin{minipage}{0.5\paperwidth}
			\centering
			\includegraphics[width=0.9\textwidth]{figs/dctcp-bic-8-0.png}
			\caption{DCTCP vs BIC with 8ms latency and 0\% loss}
			\label{fig:fair-2}
		\end{minipage}
	}
\end{figure}

@@

\begin{figure}[H]
	\centering
		\includegraphics[scale=0.4]{figs/ctcp-bic-8-0.png}
		\caption{TODO}
	\label{fig:packet-loss-chart}
\end{figure}

Additionally, CTCP also lowers its speed in response to the simulated network
circumstances: with 1.2\% packet loss and 8 milliseconds latency, it will reach
around 25 megabits, and with 290 milliseconds latency and no loss, it reaches
around 1.5 megabits. In neither case does it reach the original 55 megabits.

BBR is unique in that it barely responds to packet loss but only to delay: even
with 1.2\% loss, as long as the delay is low (8 milliseconds in our case), it
reaches 850$\pm$20 megabits per second. Other algorithms will reach much lower
speeds (24 megabits is not uncommon), but we see no signs of BBR being the
cause of that. In tests with BBR nor CTCP, speeds are not higher than when BBR
is one of the algorithms being tested.
